From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Reworked Section 3.5.x.

The next challenge concerns the data mappings between Freebase topics and properties
and Wikidata items and properties.
Two mappings between Freebase topics and Wikidata items were initially available,
and in addition to those, we worked on further mappings.
A~first one has been created by Google in October 2013%
\footnote{Freebase mappings: \url{http://developers.google.com/freebase/data}}
and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
The quality of this mapping is considered very good by the Wikidata community,
who thus have decided to use it and further curate and maintain it by hand.
It maps 1.15~million Freebase topics to their corresponding Wikidata items.
A~second actively maintained mapping has been created by Samsung.%
\footnote{Samsung mappings: \url{http://github.com/Samsung/KnowledgeSharingPlatform}}
It is based on the same idea, but matches a~Freebase topic with a~Wikidata item
even if there is only a~single shared Wikipedia link.
The precision of the mapping is naturally lower compared to Google's mapping
as there are more wrong matches (often because there is no clear separation between topics
and disambiguation pages in Wikipedia), however, the recall increases to 4.4~million~links.
As we have shown in \autoref{sec:dataquality},
human curation is required before import anyway,
which is why we have decided to merge the two mapping dumps.
For the 6,000 conflicts that appeared, we decided to prioritize Google's mapping.

@@

To improve the result, we have also done some reconciliation based on third-party database IDs
shared by Freebase and Wikidata, like MusicBrainz~\cite{musicbrainz},
VIAF~\cite{viaf}, \emph{etc.}
With this technique, we were able to match 800,000~external database IDs,
creating an additional mapping for 600,000~topics---%
most of them already in the merged version of Google's and Samsung's mappings.
Eventually, this reconciliation effort resulted in an additional 84,000 mapped items.

We also used Google's Knowledge Graph~\cite{singhal2012} to add 100,000 further mappings
by also matching a~topic and an item if they share a~Wikipedia link with the Knowledge Graph item.
There is some potential to add more data by looking at functional relations
like \textit{``father''} and \textit{``mother''},
but these relations only apply to relatively small sets of data
(like well known families), and the functional assumptions may run into some edge cases.
For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.

@@

The \emph{mapped} topics have an average number of 13.9~facts,
whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
We have mapped the majority of all topics with more than 47~facts
(191K~non mapped topics \textit{vs.} 195K~mapped topics).
This indicates that we have mapped the most important items of Freebase.
\autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
put in relation to the number of facts per item: note that the Figure is log-scaled
on both axes, so the seemingly small area between the two lines covers a~majority of
the topics. It can also be seen that there are a~very small number of topics with
a~high number of facts which have not been covered (in the lower part of the Figure).
These have all been manually inspected and found to be specific to the way knowledge
in Freebase is built. The vast majority of items with more than ten facts - in the
center of the Figure - has been mapped. The items that have not been mapped -
visible in the upper left corner of the image - are very thin,
i.e. mostly have a~very small number of facts and
would not have added much to the knowledge base.

>>>>

The next challenge concerns the data mappings between Freebase topics and properties,
and Wikidata items and properties.
Two mappings between Freebase topics and Wikidata items were initially available,
and in addition to those, we worked on further mappings.
A~first one has been created by Google in October 2013%
\footnote{Freebase mappings: \url{http://developers.google.com/freebase/data}}
and is based on Wikipedia links already present in Freebase: if a~Freebase topic and
a~Wikidata item share at least two Wikipedia links, they are assumed to describe the same subject.
The quality of this mapping is considered very good by the Wikidata community,
who thus have decided to use it and further curate and maintain it by hand.
It maps 1.15~million Freebase topics to their corresponding Wikidata items.

A~second actively maintained mapping has been created by Samsung.%
\footnote{Samsung mappings: \url{http://github.com/Samsung/KnowledgeSharingPlatform}}
It is based on the same idea, but matches a~Freebase topic with a~Wikidata item
even if there is only a~single shared Wikipedia link.
The precision of the mapping is naturally lower compared to Google's mapping,
as there are more wrong matches (often because there is no clear separation between topics
and disambiguation pages in Wikipedia), however, the recall increases to 4.4~million~links.

As we have shown in \autoref{sec:dataquality},
human curation is required before import anyway,
which is why we have decided to merge the two mapping dumps.
For the 6,000 conflicts that appeared, we decided to prioritize Google's mapping.

@@

To improve the result, we have also done some reconciliation based on third-party database IDs
shared by Freebase and Wikidata, like MusicBrainz~\cite{musicbrainz},
VIAF~\cite{viaf}, \emph{etc.}
With this technique, we were able to match 800,000~external database IDs,
creating an additional mapping for 600,000~to\-pics---%
most of them already in the merged version of Google's and Samsung's mappings.
Eventually, this reconciliation effort resulted in an additional 84,000 mapped items.

We also used Google's Knowledge Graph~\cite{singhal2012} to add about 100,000 further mappings
by also matching a~topic and an item if they share a~Wikipedia link with the Knowledge Graph item.
There is some potential to add more data by looking at functional relations
like \textit{``father''} and \textit{``mother''},
but these relations only apply to relatively small sets of data
(like well known families), and the functional assumptions may run into some edge cases.
For example, the \texttt{/people/person/parents} property in Freebase also covers stepparents,
which may create cases where a~person has more than one male or female \texttt{/people/person/parents}.

@@

The \emph{mapped} topics have an average number of 13.9~facts,
whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
We have mapped the majority of all topics with more than 47~facts
(191K~non mapped topics \textit{vs.} 195K~mapped topics).
This indicates that we have mapped the most important items of Freebase.
\autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
put in relation to the number of facts per item: note that the Figure is log-scaled
on both axes, so the seemingly small area between the two lines covers a~majority of
the topics. It can also be seen that there are a~very small number of topics with
a~high number of facts which have not been covered (in the lower part of the Figure).
These have all been manually inspected and found to be specific to the way knowledge
in Freebase is modeled. The vast majority of items with more than ten facts---in the
center of the Figure---has been mapped. The items that have not been mapped---%
visible in the upper left corner of the image---are very thin,
\emph{i.e.}, mostly have a~very small number of facts and
would not have added much to the knowledge base.
